Evaluation of performances

### 2019-09-03 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE, verbose = TRUE)

# save as latex table
table1 %>%
  ungroup() %>%
  arrange(RMSE) %>%
  slice(1:15) %>%
  xtable(
    type = "latex",
    caption = "Top 15 results for any task/learner/filter combination, sorted by performance.",
    label = "tab:perf-top-15"
  ) %>%
  print(
    file = "code/98-paper/ieee/performance-top-20.tex",
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "h!",
    caption.placement = "top",
    timestamp = NULL
  )

@@

# save as latex table
table2 %>%
  xtable(
    type = "latex",
    caption = "Best performance of each learner across any task and filter method.",
    label = "tab:best-learner-perf"
  ) %>%
  print(
    file = "code/98-paper/ieee/performance-best-per-learner.tex",
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "h!",
    caption.placement = "top",
    timestamp = NULL
  )

>>>>

# save as latex table
table1 %>%
  ungroup() %>%
  arrange(RMSE) %>%
  slice(1:15) %>%
  xtable(
    type = "latex",
    caption = "Top 15 results for any task/learner/filter combination, sorted by performance.",
    label = "tab:perf-top-15"
  ) %>%
  print(
    file = "code/98-paper/ieee/performance-top-20.tex",
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

@@

# save as latex table
table2 %>%
  xtable(
    type = "latex",
    caption = "Best performance of each learner across any task and filter method.",
    label = "tab:best-learner-perf"
  ) %>%
  print(
    file = "code/98-paper/ieee/performance-best-per-learner.tex",
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    scalebox = 0.90,
    caption.placement = "top",
    timestamp = NULL
  )
